Developmental psychology focuses on how psychological constructs change with age.  Throughout the years, many theories have been proposed to characterize and explain how and why developmental changes happen [e.g., @piaget1971theory; @bronfenbrenner1977toward; @carey2009origin; @thelen2007dynamic; @elman1996rethinking; @flavell1994cognitive]. Among these theories, one common assumption is that skills increase with age (positive change assumption): children get better as they get older. Often, researchers treat age as a predictor in linear regression models, and therefore implicitly assume that the constructs of interests follow a linear trajectory [@lindenberger1998complex]. While both assumptions are widely adopted, especially in early cognitive and language development, their validity is rarely tested. 	

One common approach to evaluating the functional form of age-related changes is through longitudinal studies. Measurements of psychological constructs, when tracked longitudinally, often reveal the age trajectories that violate the linearity assumption. For instance, a longitudinal study that follows the development of executive function (EF) from 3 to 5 years-old using a battery of EF tasks show that EF follows a non-linear trajectory over age [@johansson2016individual]. Similarly, vocabulary in early childhood, measured by MacArthur-Bates Communicative Development Inventories, also follows the exponential trend rather than the linear trend [@frank2021variability]. In many domains with established measurements, longitudinal research has been used to characterize the functional form of the development [@adolph2008shape; @mcardle2009modeling; @cole2020development; @karlberg1987analysis; @tilling2014modelling]. However, longitudinal methods are more rarely applied to experimental studies that identify proposed mechanisms underlying development. 

Many important findings in early language and cognitive development are primarily attested in cross-sectional experimental studies. For example, in the language learning domain, many studies have targeted specific mechanisms proposed to underlie how infants acquire specific facets of language. Constructs such as mutual exclusivity [@markman1988children], statistical learning [@saffran1996statistical], syntactic bootstrapping [@naigles1990children] and so on, are all attested through decades of experimental evidence acquired through cross-sectional studies. These works are critical to test the causal mechanisms underlying age-related changes, but they are rarely measured in samples with sufficient size and age variation to test the positive change assumption or the assumption of linearity [cf. @frank2017collaborative]. In an ideal world, one would run those experiments longitudinally on a large, diverse sample. In practice, this goal is difficult to achieve due to the constraints on both time and financial resources. As a result, the functional forms of age-related changes in critical constructs remain poorly understood. 

To address this issue, we turned to meta-analysis. Meta-analysis is a statistical method to aggregate evidence across studies quantitatively. This approach has been widely adopted in many disciplines and subfields, including developmental psychology [e.g. @hyde1984large; @letourneau2013socioeconomic;@doebel2015meta]. Compared to the single study approach, meta-analysis has several advantages. First, it allows us to examine the robustness of the phenomena documented in the literature. By combining results from multiple studies, meta-analysis enhances the statistical power to detect effects that might be too small to identify in individual studies. Second, meta-analysis provides a framework for assessing the consistency of research findings across different contexts [@borenstein2021introduction; @egger1997meta]. Further, pooling across developmental studies with different cross-sectional samples may yield sufficient  variation to explore the functional form of age-related change with greater precision than individual studies.

In this work, we aim to leverage meta-analysis to examine the shape of the developmental trajectory in key constructs in infant language and cognitive development. Specifically, we use existing meta-analyses from Metalab (https://langcog.github.io/metalab/), a platform that hosts community-augmented meta-analyses. Metalab was established to provide dynamic databases publicly available to all researchers [@bergmann2018promoting]. Researchers can deposit their meta-analysis dataset in the platform, and they can also use the dataset for custom analyses [e.g. @cao2023synthesis; @lewis2016quantitative]. To this date, Metalab contains #FIXME effect sizes from #FIXME different meta-analysis, spanning different areas of developmental psychology. This resource allows us to examine the suitability of meta-analysis as a tool to characterize developmental trajectory – and if suitable, provides insights into how these key constructs develop across the early months of childhood. 

We acknowledge at the outset that meta-analysis has significant limitations. The quality of a meta-analysis is necessarily constrained by the quality of the existing studies [@simonsohn2022above]. If the studies being aggregated are flawed, the conclusions drawn from the meta-analysis will also be questionable. Moreover, one significant issue in interpreting meta-analysis is the heterogeneity among studies. Heterogeneity refers to the variability in study participants, interventions, outcomes, and methodologies. This diversity can make it challenging to aggregate results meaningfully, because differences between studies may reflect true variation in effects rather than a singular underlying effect size [@fletcher2007heterogeneity;@higgins2002quantifying; @thompson1999explaining; @huedo2006assessing]. Critically, understanding the source of heterogeneity often requires detailed coding of the potential moderators; this process is frequently hampered by the inadequate reporting standards prevalent in psychological literature, which often leaves essential information for coding these moderators absent [@publications2008reporting;@nicholson2017attrition]. In other words, whether meta-analysis can provide insights into the nature of age-related change is dependent upon the quality of the existing literature.

This paper is organized as follows. In the first section, we provide an overview on the estimated general shape of age-related change across the datasets in Metalab. To preview our findings, we found that most datasets showed relatively constant effect size across age. This finding challenges the commonly held linearity assumption and the positive increase assumption. In the second section, we test four hypotheses on why the current meta-analyses failed to reveal age-related changes: (1) age-related selection bias against younger infants; (2) methodological adaptation for older infants; (3) change in only a subset of conditions; and (4) positive growth only after infancy. We found that none of the four explanations provided a satisfying explanation for the lack of age-related change in most meta-analyses. 


```{r results = "asis"}
table_1 <- readRDS(here("writing/display_items/table_1.Rds"))
#table_1 %>% papaja::apa_table(landscape = TRUE, longtable = TRUE)
```

\begin{lltable}

\begin{longtable}{llllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:unnamed-chunk-12} This table summarizes the number of effect sizes (ES) and the number of participants included in each dataset. The ES estimates represent the aggregated effect sizes and their 95\% confidence intervals. The $I^2$ measures the heterogneity of each dataset. The paper source column indicates the published record associated with each dataset.}\\
\toprule
Dataset & \multicolumn{1}{c}{N ES} & \multicolumn{1}{c}{N Subject} & \multicolumn{1}{c}{MA ES} & \multicolumn{1}{c}{$I^2$} & \multicolumn{1}{c}{Source paper}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:unnamed-chunk-12} continued}}\\
\toprule
Dataset & \multicolumn{1}{c}{N ES} & \multicolumn{1}{c}{N Subject} & \multicolumn{1}{c}{MA ES} & \multicolumn{1}{c}{$I^2$} & \multicolumn{1}{c}{Source paper}\\
\midrule
\endhead
Abstract rule learning & 95 & 1123 & 0.22 [0.07, 0.37] & 0.80 & Rabagliati et al., (2018)\\
Audio-visual congruence & 92 & 4132 & 0.33 [0.19, 0.47] & 0.89 & Cox et al., (2022)\\
Categorization bias & 80 & 594 & 0.16 [-0.66, 0.99] & 0.96 & NA\\
Cross-situational word learning & 48 & 2241 & 0.67 [0.5, 0.84] & 0.90 & NA\\
Familiar word recognition & 34 & 586 & 0.54 [0.38, 0.69] & 0.55 & Carbajal et al., (2021)\\
Gaze following (combined) & 81 & 1407 & 0.81 [0.61, 1.01] & 0.90 & Frank et al., (2016)\\
Infant directed speech preference & 100 & 1267 & 0.37 [0.25, 0.49] & 0.71 & Zettersten et al., (2023)\\
Label advantage in concept learning & 100 & 1644 & 0.36 [0.23, 0.48] & 0.73 & NA\\
Language discrimination & 104 & 1479 & -0.26 [-0.4, -0.11] & 0.77 & Gasparini et al., (2021)\\
Language preference & 49 & 641 & 0.11 [-0.06, 0.28] & 0.93 & Gasparini et al., (2021)\\
Mispronunciation sensitivity & 249 & 2122 & 0.45 [0.24, 0.66] & 0.94 & Von Holzen \& Bergmann (2021)\\
Mutual exclusivity & 131 & 2222 & 1.27 [0.99, 1.56] & 0.95 & Lewis et al. (2020)\\
Natural speech preference & 55 & 786 & 0.44 [0.23, 0.65] & 0.83 & Issard et al., (2023)\\
Neonatal Imitation & 336 & 2455 & 0.68 [0.4, 0.97] & 0.94 & Davis et al. (2021)\\
Online word recognition & 14 & 330 & 1.37 [0.78, 1.96] & 0.95 & Frank et al., (2016)\\
Prosocial agents & 61 & 1244 & 0.4 [0.29, 0.52] & 0.20 & Margoni \& Surian (2018)\\
Simple arithmetic competences & 14 & 369 & 0.25 [0.04, 0.46] & 0.54 & Christodoulou et al., (2017)\\
Sound symbolism & 44 & 425 & 0.16 [-0.01, 0.33] & 0.69 & Fort et al. (2018)\\
Statistical sound category learning & 20 & 591 & 0.29 [0.01, 0.57] & 0.58 & Cristia (2018)\\
Statistical word segmentation & 103 & 804 & -0.08 [-0.18, 0.02] & 0.83 & Black \& Bergmann (2017)\\
Switch task & 143 & 2764 & -0.16 [-0.25, -0.06] & 0.78 & Tsui et al., (2019)\\
Syntactic bootstrapping & 60 & 832 & 0.24 [0.03, 0.44] & 0.72 & Cao \& Lewis (2022)\\
Vowel discrimination (native) & 143 & 2418 & 0.59 [0.43, 0.75] & 0.78 & Tsuji \& Cristia (2014)\\
Vowel discrimination (non-native) & 49 & 600 & 0.65 [0.2, 1.1] & 0.92 & Tsuji \& Cristia (2014)\\
Word segmentation (combined) & 315 & 2910 & 0.2 [0.14, 0.26] & 0.78 & Bergmann \& Cristia (2016)\\
\bottomrule
\end{longtable}

\end{lltable}


 
```{r}
table_2 <- readRDS(here("writing/display_items/table_2.Rds"))
#table_2 %>% papaja::apa_table()
```
 
\begin{table*}[hbt]
\ifnextchar[{\eatarg}{}
[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-10} This table summarizes the values of $\Delta$ of corrected Akaike Information Criterion (AICc) for the age model with different functional forms: Constant, Linear, Logarithmic, and Quadratic. The values were calculated from subtracting the minimum AICc from the AICc of each model. They were rounded to two decimal. The bold values indicate the best fitting model. Asterisks indicate models that are a significantly better fit compared to other functional forms for that dataset.}

\begin{tabular}{lllll}
\toprule
Dataset & \multicolumn{1}{c}{Const} & \multicolumn{1}{c}{Linear} & \multicolumn{1}{c}{Log} & \multicolumn{1}{c}{Quadratic}\\
\midrule
Cross-situational word learning & \bf{0.00} & 2.44 & 2.29 & 2.55\\
Language discrimination & \bf{0.00} & 1.32 & 0.91 & 1.59\\
Prosocial agents & \bf{0.00} & 2.08 & 1.87 & 2.15\\
Simple arithmetic competences & \bf{0.00*} & 6.65* & 6.74* & 6.55*\\
Statistical word segmentation & \bf{0.00} & 1.34 & 1.51 & 1.12\\
Switch task & \bf{0.00} & 1.12 & 1.15 & 1.06\\
Syntactic bootstrapping & \bf{0.00} & 0.71 & 0.56 & 0.88\\
Vowel discrimination (native) & \bf{0.00} & 1.34 & 0.99 & 1.63\\
Vowel discrimination (non-native) & \bf{0.00} & 1.56 & 1.67 & 1.46\\
Word segmentation (combined) & \bf{0.00} & 1.28 & 1.05 & 1.61\\
Infant directed speech preference & \bf{0.00} & 1.57 & 1.47 & 1.53\\
Mispronunciation sensitivity & 1.89 & \bf{0.00} & 0.05 & 0.19\\
Online word recognition & 2.22 & \bf{0.00} & 0.23 & 0.15\\
Sound symbolism & 3.91 & \bf{0.00} & 0.61 & 0.09\\
Audio-visual congruence & 5.90* & 6.70* & \bf{0.00*} & 7.44*\\
Label advantage in concept learning & 2.37 & 0.95 & \bf{0.00} & 1.63\\
Mutual exclusivity & 9.80* & 0.58 & \bf{0.00*} & 1.38\\
Neonatal Imitation & 2.25 & 0.36 & \bf{0.00} & 1.06\\
Abstract rule learning & 0.44 & 0.32 & 0.86 & \bf{0.00}\\
Categorization bias & 8.46* & 0.62 & 1.36 & \bf{0.00*}\\
Familiar word recognition & 1.68 & 0.28 & 1.15 & \bf{0.00}\\
Gaze following (combined) & 43.73* & 2.07 & 10.41* & \bf{0.00*}\\
Language preference & 2.50 & 2.36 & 4.12 & \bf{0.00}\\
Natural speech preference & 0.86 & 0.43 & 1.04 & \bf{0.00}\\
Statistical sound category learning & 3.44 & 1.04 & 3.01 & \bf{0.00}\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table*}
\efloatseparator
