---
title: "author_exploration"
author: "anjie"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyverse)
library(here)
library(broom)
library(metafor)
library(ggthemes)


source(here("helper/author_help.r"))

d <- read_csv(here("data/clean_data.csv"))
author_d <- read_csv(here("data/clean_author.csv"))
```


# Visuralization


## Abstract rule learning"  

```{r}
visualize_major_author_effect(d, "Abstract rule learning", author_d)

```

## Categorization bias


```{r}
visualize_major_author_effect(d, "Categorization bias", author_d)
visualize_major_author_effect(d, "Categorization bias", author_d, age_limit = TRUE)


```

## Cross-situational word learning



```{r}
visualize_major_author_effect(d,"Cross-situational word learning", author_d)

visualize_major_author_effect(d,"Cross-situational word learning", author_d, TRUE)

```


## Familiar word recognition    

```{r}
visualize_major_author_effect(d,"Familiar word recognition", author_d)
visualize_major_author_effect(d,"Familiar word recognition", author_d, TRUE)

```

## Gaze following (combined)

methodologically moderated?
early author???

```{r}
visualize_major_author_effect(d,"Gaze following (combined)", author_d)
visualize_major_author_effect(d,"Gaze following (combined)", author_d, TRUE)


```

## Infant directed speech preference 

first proxy for mean age months, not accurate

method? 
non-native langauge?

```{r}


ids_author <- author_d %>% 
  filter(percent_by_author > .15) %>% 
  filter(ds_clean == "Infant directed speech preference")
  
  

ids <- lapply(ids_author$author_clean, 
       function(name){
         
         d %>% 
          filter(ds_clean == "Infant directed speech preference") %>% 
          mutate(
          by_major_author = case_when(
             grepl(name, long_cite) ~ "yes", 
             !grepl(name, long_cite) ~ "no"
            )
          ) %>% 
  #filter(ds_clean %in% c("Mispronunciation sensitivity", "Prosocial agents")) %>% 
          #filter(mean_age_months < 36) %>% 
          mutate(major_author = name)
                 
       }) %>% 
  bind_rows()
 

ids %>% 
  filter(mean_age_months < 12) %>% 
   ggplot(aes(x = mean_age_months, y = d, color = by_major_author))+
          geom_point() + 
          geom_smooth(method = "lm") + 
  facet_wrap(~major_author) + 
  labs(title ="Infant directed speech preference") 

```


## Label advantage in concept learning         

```{r}
visualize_major_author_effect(d,"Label advantage in concept learning", author_d)
visualize_major_author_effect(d,"Label advantage in concept learning", author_d, TRUE)

```

## Language discrimination and preference



```{r}
visualize_major_author_effect(d,"Language discrimination and preference", author_d)
visualize_major_author_effect(d,"Language discrimination and preference", author_d, TRUE)

```

## Mispronunciation sensitivity

```{r}
visualize_major_author_effect(d,"Mispronunciation sensitivity" , author_d)
visualize_major_author_effect(d,"Mispronunciation sensitivity" , author_d, TRUE)
```



## Mutual exclusivity

```{r}
visualize_major_author_effect(d,"Mutual exclusivity"  , author_d)
visualize_major_author_effect(d,"Mutual exclusivity"  , author_d, TRUE)

```

## Natural speech preference 
 
```{r}
visualize_major_author_effect(d,"Natural speech preference"  , author_d)
visualize_major_author_effect(d,"Natural speech preference"  , author_d, TRUE)


```
 
## Online word recognition       

```{r}
visualize_major_author_effect(d,"Online word recognition"  , author_d)
visualize_major_author_effect(d,"Online word recognition"  , author_d, TRUE)

```

## Prosocial Agents

doesn't have long cite so can only rely on Hamlin

```{r}
d %>%
  filter(ds_clean == "Prosocial agents") %>% 
  mutate(hamlin_lab = ifelse(Hamlin_Lab == 1, "by_hamlin", "not_by_hamlin")) %>% 
   ggplot(aes(x = mean_age_months, y = d_calc, color = hamlin_lab, group = hamlin_lab))+
          geom_point() + 
          geom_smooth(method = "lm") +
  labs(title ="Prosocial agents")
```


## Simple arithmetic competences"     

```{r}
visualize_major_author_effect(d,"Simple arithmetic competences" , author_d)
visualize_major_author_effect(d,"Simple arithmetic competences" , author_d, TRUE)


```

## sound symbolism

```{r}
visualize_major_author_effect(d,"Sound symbolism" , author_d)
visualize_major_author_effect(d,"Sound symbolism" , author_d, TRUE)

```

## Statistical sound category learning (habituation)

```{r}



sscl_d <- author_d %>% 
  filter(percent_by_author > .15) %>% 
  filter(ds_clean == "Statistical sound category learning (habituation)") %>% 
  mutate(author_clean = case_when(
    author_clean == "vanZuijen" ~ "van Zuijen", 
    author_clean == "MayeJ" ~ "Maye J", 
    author_clean == "WeissDJ" ~ "Weiss DJ", 
    TRUE ~ author_clean 
  ))
  
  
sscl_d <- lapply(sscl_d$author_clean, 
       function(name){
         d %>% 
          filter(ds_clean == "Statistical sound category learning (habituation)") %>% 
          mutate(
          by_major_author = case_when(
             grepl(name, long_cite) ~ "yes", 
             !grepl(name, long_cite) ~ "no"
            )
          ) %>%
          mutate(major_author = name)
       }) %>% 
  bind_rows()


sscl_d %>% 
   ggplot(aes(x = mean_age_months, y = d_calc, color = by_major_author))+
          geom_point() + 
          geom_smooth(method = "lm") + 
  facet_wrap(~major_author) + 
  labs(title ="Mispronunciation sensitivity")


```


## Statistical word segmentation    

```{r}
visualize_major_author_effect(d,"Statistical word segmentation" , author_d)
visualize_major_author_effect(d,"Statistical word segmentation" , author_d, TRUE)

```


## Switch task

```{r}
visualize_major_author_effect(d,"Switch task" , author_d)
visualize_major_author_effect(d,"Switch task" , author_d, TRUE)

```

## Symbolic play

```{r}
visualize_major_author_effect(d,"Symbolic play" , author_d)
visualize_major_author_effect(d,"Symbolic play" , author_d, TRUE)

```

## Syntactic bootstrapping
 
```{r}
visualize_major_author_effect(d,"Syntactic bootstrapping" , author_d)
visualize_major_author_effect(d,"Syntactic bootstrapping" , author_d, TRUE)

```

## Vowel discrimination (native)

```{r}
visualize_major_author_effect(d,"Vowel discrimination (native)" , author_d)
visualize_major_author_effect(d,"Vowel discrimination (native)" , author_d, TRUE)

```

## Vowel discrimination (non-native)

odd datapoints?

```{r}
visualize_major_author_effect(d,"Vowel discrimination (non-native)" , author_d)
visualize_major_author_effect(d,"Vowel discrimination (non-native)" , author_d, TRUE)


```

## Word Segmentation (combined)

```{r}
visualize_major_author_effect(d,"Word Segmentation (combined)" , author_d)
visualize_major_author_effect(d,"Word Segmentation (combined)" , author_d, TRUE)

```




# run all the lm

```{r}
# unique ls of dataset name 

all_nested_d <-lapply(distinct(d, ds_clean) %>% pull(), 
       function(x){
         get_major_author_effect(d, x, author_d)
       }) %>% 
  bind_rows() %>% 
  group_by(ds_clean, major_author) %>% 
  nest()



```


```{r}

missing_info_ds <- d %>%   
  filter(is.na(unique_row) | is.na(same_infant) | is.na(short_cite)) %>%  
  distinct(ds_clean) %>% 
  pull(ds_clean)
```


```{r}
all_rma_models <- all_nested_d %>% 
  filter(!ds_clean %in% missing_info_ds) %>% 
  filter(!major_author %in% c("…SweigWilson", "deVilliers", "Fernald","GrafEstes"
                              )) %>% 
  filter(!is.na(major_author) & ds_clean != "Prosocial Agents") %>% 
  # fail to converge 
  filter(ds_clean != "Familiar word recognition") %>% 
  filter(ds_clean != "Symbolic play") %>% 
  mutate(mod = map(data, function (df) rma.mv(
    d_calc ~ mean_age_months * by_major_author, 
    V = d_var_calc, 
    random = ~ 1 | short_cite/same_infant/unique_row, 
    method = "REML", 
    data = df)), 
    tidy = map(mod, broom::tidy)) %>% 
  select(-mod, -data) %>% 
  unnest(tidy)


pruned_models_df <- all_nested_d %>% 
  filter(ds_clean == "Familiar word recognition" | 
         ds_clean == "Symbolic play") %>% 
  mutate(mod = map(data, function (df) rma.mv(
    d_calc ~ mean_age_months * by_major_author, 
    V = d_var_calc, 
    random = ~ 1 | short_cite/same_infant, 
    method = "REML", 
    data = df)), 
    tidy = map(mod, broom::tidy)) %>% 
  select(-mod, -data) %>% 
  unnest(tidy)


rmamv_df <- bind_rows(all_rma_models, pruned_models_df)

```

```{r}
significant_author_df <- rmamv_df %>% 
  filter(p.value < 0.05) %>% 
  filter(grepl("author", term)) %>% 
  distinct(ds_clean, major_author)
```

```{r}
all_nested_d %>% 
  filter(ds_clean %in% significant_author_df$ds_clean, 
         major_author %in% significant_author_df$major_author) %>% 
  unnest(data) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = by_major_author))+
    geom_point() + 
    geom_smooth(method = "lm") + 
    facet_wrap(ds_clean~major_author)
```


# Method check 

could method variation explain the major eauthor effect? 

## Abstract rule learning + Ferguson

```{r}
arl_d<-all_nested_d %>% 
  filter(ds_clean == "Abstract rule learning", major_author == "Ferguson") %>% 
  unnest(data) 


arl_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = by_major_author))+
    geom_point() + 
    geom_smooth(method = "lm")
```
```{r}


m <- c("long_cite", "by_major_author", "response_mode", 
         "exposure_phase", "method", "dependent_measure", "participant_design", 
         "native_lang", "test_lang", 
         "Modality", "Semantics", "TrainingRule")

visualize_method_diff(arl_d, m)
```




when controlling for the methodologies it still significant?

```{r}
  rma.mv(
    d_calc ~ mean_age_months * by_major_author + exposure_phase + method + Modality, 
    V = d_var_calc, 
    random = ~ 1 | short_cite/same_infant/unique_row, 
    method = "REML", 
    data = arl_d) %>% 
  tidy()
```


## Familiar word recognition 

```{r}
fwr_d<-all_nested_d %>% 
  filter(ds_clean == "Familiar word recognition", major_author == "Hallé") %>% 
  unnest(data) 


fwr_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = by_major_author))+
    geom_point() + 
    geom_smooth(method = "lm")
```


didn't see a big difference tbh?

```{r}

fwr_m <- c("long_cite", "by_major_author", "response_mode", 
         "exposure_phase", "method", "dependent_measure", "participant_design", 
         "native_lang", "infant_type", "test_lang", "tokens_per_trial", "word_types_per_cond",
         "publication_type")


visualize_method_diff(fwr_d, fwr_m)


```
just look at method, still significant 

```{r}
 rma.mv(
    d_calc ~ mean_age_months * by_major_author + method , 
    V = d_var_calc, 
    random = ~ 1 | short_cite/same_infant/unique_row, 
    method = "REML", 
    data = fwr_d) %>% 
  tidy()
```

## Gaze following 


```{r}
gf_d<-all_nested_d %>% 
  filter(ds_clean == "Gaze following (combined)", major_author == "Delgado") %>% 
  unnest(data) 


gf_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = by_major_author))+
    geom_point() + 
    geom_smooth(method = "lm")
```
```{r}
gf_d %>% 
  ungroup() %>% 
  select(long_cite) %>% 
  filter(grepl("Delgado", long_cite)) %>% 
  distinct() 
  

gf_d %>% 
  ungroup() %>% 
  select(long_cite) %>% 
  filter(grepl("Mundy", long_cite)) %>% 
  distinct() 

gf_d %>% 
  ungroup() %>% 
  select(long_cite) %>% 
  filter(grepl("Mundy", long_cite) & grepl("Delgado", long_cite)) %>% 
  distinct() 
```


```{r}
gf_m <- c("long_cite", "by_major_author", "response_mode", "exposure_phase", "method", 
          "dependent_measure", "participant_design", "native_lang", "infant_type", "num_trials", 
          "cue_type")

visualize_method_diff(gf_d, gf_m)
```
```{r}
rma.mv(
    d_calc ~ mean_age_months * by_major_author + cue_type , 
    V = d_var_calc, 
    random = ~ 1 | short_cite/same_infant/unique_row, 
    method = "REML", 
    data = gf_d) %>% 
  tidy()
```

## Mispronunciation sensitivity 

```{r}
ms_d <- all_nested_d %>% 
filter(ds_clean == "Mispronunciation sensitivity", major_author == "Swingley") %>% 
  unnest(data) 


ms_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = by_major_author))+
    geom_point() + 
    geom_smooth(method = "lm")
```

```{r}
ms_d
```


really doesn't see much that's off 

```{r}
ms_m <- c("long_cite", "by_major_author", "response_mode", "exposure_phase", "method", 
          "CorrectPronunciation", "Mispronunciation", "is_correct", "n_feature", "type_feature", 
          "mispron_location")

visualize_method_diff(ms_d, ms_m)
```

