---
title: "03_moderators"
author: "anjie"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: yes
    theme: paper
    toc: yes
    toc_float: yes
---


```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


```{r}
library(tidyverse)
library(here)
library(ggthemes)
library(metafor)
library(kableExtra)
library(ggrepel)

d <- read_csv(here("data/metalab_data_mini.csv"))
author_d <- read_csv(here("data/clean_author.csv"))

source(here("helper/model_comparison_help.r"))
source(here("helper/method_mod_help.r"))
source(here("helper/author_help.r"))



best_fit_bmeasure_model_df <- readRDS(here("cached_data/best_fit_behavioral_measure_df.Rds"))
best_fit_ep_model_df <- readRDS(here("cached_data/best_fit_exposure_phase.Rds"))
best_fit_sn_model_df <- readRDS(here("cached_data/best_fit_stimuli_naturalness.Rds"))
best_fit_major_author_df <- readRDS(here("cached_data/best_fit_major_author_df.Rds"))

age_modesl_df <- readRDS(here("cached_data/age_models_df.Rds"))

major_author_fit_df <- readRDS(here("cached_data/major_author_model_ds.Rds"))


```





# 1. behavioral_measure 


## running  models for comparison

```{r eval=FALSE, include=FALSE}
d <- d %>% mutate(behavioral_measure = as.factor(behavioral_measure))
d$behavioral_measure <-  relevel(d$behavioral_measure, ref="looking")

# getting the subset of data
bmeasure_ds <- d %>% 
  filter(!response_mode %in% c("NIRS", "EEG")) %>% 
  distinct(ds_clean, behavioral_measure) %>% 
  group_by(ds_clean) %>% 
  count() %>% 
  filter(!n == 1) %>% 
  pull(ds_clean)



# for model fits
bmeasure_models_df <- lapply(bmeasure_ds, 
       function(name){
         print(name)
         get_compare_IC_df( d %>% 
  filter(!response_mode %in% c("NIRS", "EEG")) , 
  name, c("behavioral_measure"))
       }) %>% 
  bind_rows() %>% 
  mutate(model_type = "bmeasure")


# finding the best fit models when adding method moderator 
min_AICc_bmeasure_df <- bmeasure_models_df %>% 
  filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) 

# finding the stats of the models 
bmeasure_models_fits_df <- lapply(bmeasure_ds, 
       function(name){
         print(name)
         get_model_fit_df( d %>% 
  filter(!response_mode %in% c("NIRS", "EEG")), name, c("behavioral_measure"))
       }) %>% 
  bind_rows()


# finding the best fit behavioral model 
best_fit_bmeasure_model_df <- bmeasure_models_fits_df %>% 
  left_join(min_AICc_bmeasure_df, 
            by =  c("model_spec", "dataset", "model_spec_clean")) %>% 
  filter(!is.na(REML)) 

saveRDS(best_fit_bmeasure_model_df, here("cached_data/best_fit_behavioral_measure_df.Rds"))
```



```{r eval=FALSE, include=FALSE}
## w/ interaction
#CURRENTLY NOT RUNNING, RAN INTO CONVERGENCE ISSUE

# getting the subset of data
bmeasure_ds <- d %>% 
  distinct(ds_clean, behavioral_measure) %>% 
  group_by(ds_clean) %>% 
  count() %>% 
  filter(!n == 1) %>% 
  pull(ds_clean)

# for model fits
bmeasure_models_interaction_df <- lapply(bmeasure_ds, 
       function(name){
         print(name)
         get_compare_IC_interaction_df(d, name, c("behavioral_measure"))
       }) %>% 
  bind_rows() %>% 
  mutate(model_type = "bmeasure_interaction")


# finding the best fit models when adding method moderator 
min_AICc_bmeasure_df <- bmeasure_models_interaction_df %>% 
  filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) 

# finding the stats of the models 
bmeasure_models_interaction_fits_df <- lapply(bmeasure_ds, 
       function(name){
         print(name)
         get_model_fit_interaction_df(d, name, c("behavioral_measure"))
       }) %>% 
  bind_rows()


# finding the best fit behavioral model 
best_fit_bmeasure_interaction_model_df <- bmeasure_models_interaction_fits_df %>% 
  left_join(min_AICc_bmeasure_df, 
            by =  c("model_spec", "dataset", "model_spec_clean")) %>% 
  filter(!is.na(REML)) 

saveRDS(best_fit_bmeasure_interaction_model_df,here("cached_data/best_fit_behavioral_measure_interaction_df.Rds"))
```


```{r eval=FALSE, include=FALSE}
best_fit_bmeasure_interaction_model_df %>% 
  filter(grepl("mean_age_months", term) & grepl("behavioral_measure", term))
```


## model stats for significant values




```{r}
best_fit_bmeasure_model_df %>% 
  filter(grepl("behavioral_measure", term)) %>% 
  #filter(p.value < .05) %>% 
  kableExtra::kable(digits = .5) %>%  
  kableExtra::kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "500px")
```

## visualization 

```{r}
best_fit_bmeasure_model_df 
```


```{r}
d %>% 
  filter(mean_age_months < 36) %>% 
  filter(ds_clean %in% unique(best_fit_bmeasure_model_df$dataset)) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = behavioral_measure)) + 
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm") + 
  facet_wrap(~ds_clean)+ 
  theme_few()
```



# 2. Exposure phase 

## running models for comparison

```{r eval=FALSE, include=FALSE}
d <- d %>% mutate(exposure_phase = as.factor(exposure_phase))
d$exposure_phase <-  relevel(d$exposure_phase, ref="familiarization")


## get subset of data
ep_d <-d %>% 
  filter(!response_mode %in% c("NIRS", "EEG")) %>% 
  distinct(ds_clean, exposure_phase) %>% 
  filter(!exposure_phase %in% c("test_only", "not_applicable")) %>% 
  group_by(ds_clean) %>% 
  count() %>% 
  filter(!n == 1) %>% 
  filter(!ds_clean %in% c("Natural speech preference")) %>% 
  pull(ds_clean)

## get model comparison stats
ep_models_df <- lapply(ep_d, 
       function(name){
         print(name)
         get_compare_IC_df( d %>% 
  filter(!response_mode %in% c("NIRS", "EEG")) %>%  filter(!exposure_phase %in% c("test_only", "not_applicable")) , name, c("exposure_phase"))
       }) %>% 
  bind_rows() %>% 
  mutate(model_type = "ep")

## find best fitting models 
min_AICc_ep_models_df <- ep_models_df %>% 
  filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) 

## finding the stats of the models 
ep_models_fits_df <- lapply(ep_d, 
       function(name){
         print(name)
         get_model_fit_df( d %>% 
  filter(!response_mode %in% c("NIRS", "EEG")) %>%  filter(!exposure_phase %in% c("test_only", "not_applicable")) , name, c("exposure_phase"))
       }) %>% 
  bind_rows()

## find the best fit model's stats
best_fit_ep_model_df <- ep_models_fits_df %>% 
  left_join(min_AICc_ep_models_df, 
            by =  c("model_spec", "dataset", "model_spec_clean")) %>% 
  filter(!is.na(REML)) 

saveRDS(best_fit_ep_model_df, here("cached_data/best_fit_exposure_phase.Rds"))
```

## model stats for significant values

```{r}
best_fit_ep_model_df %>% 
  filter(grepl("exposure_phase", term)) %>% 
  filter(p.value < .05) %>% 
  kableExtra::kable(digits = .2) %>%  
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "500px")
```

## visualization

```{r}
d %>% 
  filter(mean_age_months < 36) %>% 
  filter(ds_clean %in% unique(best_fit_ep_model_df$dataset)) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = exposure_phase)) + 
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm") + 
  facet_wrap(~ds_clean)+ 
  theme_few()
```



# 3. Stimuli naturalness 

```{r}
## get subset of data
sn_d <- d %>% 
  distinct(ds_clean, stimuli_naturalness) %>% 
  filter(!is.na(stimuli_naturalness)) %>% 
  group_by(ds_clean) %>% 
  count() %>% 
  filter(!n == 1) %>% 
  pull(ds_clean)

## get model comparison stats
sn_models_df <- lapply(sn_d, 
       function(name){
         print(name)
         get_compare_IC_df(d %>% filter(!is.na(stimuli_naturalness)), name, c("stimuli_naturalness"))
       }) %>% 
  bind_rows() %>% 
  mutate(model_type = "sn")

## find best fitting models 
min_AICc_sn_models_df <- sn_models_df %>% 
  filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) 

## finding the stats of the models 
sn_models_fits_df <- lapply(sn_d, 
       function(name){
         print(name)
         get_model_fit_df(d %>% filter(!is.na(stimuli_naturalness)), name, c("stimuli_naturalness"))
       }) %>% 
  bind_rows()

## find the best fit model's stats
best_fit_sn_model_df <- sn_models_fits_df %>% 
  left_join(min_AICc_sn_models_df, 
            by =  c("model_spec", "dataset", "model_spec_clean")) %>% 
  filter(!is.na(REML)) 

saveRDS(best_fit_sn_model_df, here("cached_data/best_fit_stimuli_naturalness.Rds"))
```



### significant models  

```{r}
best_fit_sn_model_df %>% 
  filter(grepl("naturalness", term)) %>% 
  filter(p.value < 0.05) %>% 
  kableExtra::kable(digits = .2) %>%  
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "500px")
```


# Collective 

```{r}
source(here("helper/plot_moderator_help.r"))

vis_df <- bind_rows(best_fit_bmeasure_model_df, 
          best_fit_ep_model_df, 
          best_fit_sn_model_df) %>% 
  mutate(lb = estimate - 1.96 * std.error, 
         ub = estimate + 1.96 * std.error) %>% 
  select(model_type, dataset, term, estimate, lb, ub)


vis_df %>% 
  filter(grepl("behavioral_measure", term) | grepl("exposure_phase", term)| grepl("stimuli_naturalness", term)) %>% 
  ggplot(aes(x = dataset, y = estimate, group = term)) + 
  geom_pointrange(aes(ymin = lb, ymax = ub)) + 
  facet_wrap(~model_type, scales = "free") + 
  theme_few()
```




# 4. Major author 

```{r}
all_nested_d <-lapply(distinct(d, ds_clean) %>% pull(), 
       function(x){
         get_major_author_effect(d, x, author_d)
       }) %>% 
  bind_rows() %>% 
  group_by(ds_clean, major_author) %>% 
  nest() %>% 
  filter(!major_author %in% c("…SweigWilson", "deVilliers", "Fernald","GrafEstes", "HillairetdeBoisferon"
                              )) %>% 
  filter(!is.na(major_author) & ds_clean != "Prosocial Agents")

```

```{r eval=FALSE, include=FALSE}
major_author_model_ds <- lapply(seq(1, nrow(all_nested_d)), 
            function(x){
              print(x)
              print( all_nested_d$ds_clean[[x]])
              get_author_model_comparison(all_nested_d, all_nested_d$ds_clean[[x]], 
                                          all_nested_d$major_author[[x]])
            }) %>% 
  bind_rows()

saveRDS(major_author_model_ds, here("cached_data/major_author_model_ds.Rds"))
```

```{r eval=FALSE, include=FALSE}
major_author_model_fits_ds <-  lapply(seq(1, nrow(all_nested_d)), 
            function(x){
              print(x)
              get_author_model_fits(all_nested_d, all_nested_d$ds_clean[[x]], 
                                          all_nested_d$major_author[[x]])
            }) %>% 
  bind_rows()

saveRDS(major_author_model_fits_ds, here("cached_data/major_author_fits_ds.Rds"))

```


## get the best fit major author models

```{r}
major_author_fit_df <- readRDS(here("cached_data/major_author_model_ds.Rds"))

major_author_model_fit_df <- readRDS(here("cached_data/major_author_fits_ds.Rds"))
```


```{r eval=FALSE, include=FALSE}
min_AICc_major_author <- major_author_fit_df %>% 
  filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) 

best_fit_major_author_model <- major_author_model_fits_ds %>% 
    left_join(min_AICc_major_author, 
              by =  c("model_spec", "dataset", "model_spec_clean", "major_author")) %>% 
    filter(!is.na(REML)) 

saveRDS(best_fit_major_author_model, here("cached_data/best_fit_major_author_df.Rds"))
```


## get the significant value 

```{r}
best_fit_major_author_model <- readRDS(here("cached_data/best_fit_major_author_df.Rds"))

best_fit_major_author_model %>% 
  filter(grepl("by_major_author", term), 
         p.value < 0.05) 
```

```{r}
source(here("helper/author_help.r"))
ma_df <- best_fit_major_author_model %>% 
  mutate(lb = estimate - 1.96 * std.error, 
         ub = estimate + 1.96 * std.error) %>% 
  filter(grepl("by_major", term)) 

plot_major_author(ma_df) 
  
```


```{r}


best_fit_major_author_model %>% 
  filter(grepl("by_major_author", term), 
         p.value < 0.05) %>% 
  kableExtra::kable(digits = .2) %>%  
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "500px") 
```

## visualization: not sure what's the best way to do it




```{r eval=FALSE, include=FALSE}


# 5. Conflict between best fit models 

## AICc vs BIC

aic_winner_df <- age_modesl_df %>% 
  filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) %>% 
  select(dataset, model_spec_clean, REML) %>% 
  rename(AICc_winner = model_spec_clean, 
         AIC_val = REML)

bic_winner_df <-  age_modesl_df %>% 
  filter(ic == "BIC") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) %>% 
  select(dataset, model_spec_clean, REML) %>% 
  rename(BIC_winner = model_spec_clean, 
         BIC_val = REML)

aic_winner_df %>% 
  left_join(bic_winner_df, by = c("dataset")) %>% 
  filter(!AICc_winner == BIC_winner) %>% 
  kableExtra::kable(digits = .2) %>%  
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "500px")
```





```{r eval=FALSE, include=FALSE}

## AICc: age vs age + moderators


#some discrepancies but not a lot 
#some have improvements and others do not 

bind_rows(best_fit_bmeasure_model_df %>% mutate(add_mod = "bmeasure"), 
          best_fit_exposure_phase_df %>% mutate(add_mod = "exp_phase"), 
          best_fit_real_visual_df %>% mutate(add_mod = "visual_stimulus"),
          best_fit_real_aud_df %>% mutate(add_mod = "auditory_stimulus"), 
          best_fit_major_author_df %>% mutate(add_mod = "by_major_author")) %>% 
  select(dataset, model_spec_clean, REML, add_mod, major_author) %>% 
  distinct(dataset, model_spec_clean, REML, add_mod, major_author) %>% 
  rename(
    add_mod_winner_model = model_spec_clean, 
    add_mod_AICc = REML
  ) %>% 
  left_join(age_modesl_df %>% 
              filter(ic == "AICc") %>%
              group_by(dataset) %>% 
              filter(REML == min(REML)) %>% 
              rename(age_AICc = REML, 
                     age_winner_model = model_spec_clean)
              , by = c("dataset")) %>% 
  select(dataset, add_mod, add_mod_winner_model, add_mod_AICc, 
         age_AICc, age_winner_model) %>% 
  filter(add_mod_winner_model != age_winner_model) %>% 
  kableExtra::kable(digits = .2) %>%  
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%", height = "500px")
```




