---
title: "05_variability.Rmd"
author: "Anjie Cao, Molly Lewis, and Michael Frank"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyverse)
library(here)
library(ggthemes)
library(metafor)
library(PublicationBias)

source(here("helper/summary_table_help.r"))
d <- read_csv(here("data/metalab_data_kitchensink.csv"))
```

# Get CV for each domain 

```{r}
summary_d <- d %>% 
  group_by(ds_clean) %>% 
  nest(data = -ds_clean) %>% 
  mutate(mod = map(data, get_ma_effect_size), 
         descriptive = map(data, get_descriptive_stas)) %>% 
  unnest(c(mod, descriptive)) %>% 
  select(-data)
```


```{r}
summary_d %>% 
  arrange(-i2) %>% 
  select(ds_clean, i2)
```





# Look at individual dataset

```{r}
sub_d <- d %>% 
  filter(ds_clean == "Categorization bias")
cols = c("infant_type", "infant_type_clincal", "infant_type_language", "n_1", "mean_age_1", "x_1", "x_2", "SD_1", "t",  "dataset", "short_name", "domain", "n", "year")


level_summary_df <- sub_d %>% 
  # get rid of the ones with all blank space
  select(!any_of(sub_d %>% keep(~all(is.na(.x))) %>% names)) %>% 
  # actually also wanted to get rid of all the ones with ANY blank space (to make sure i2 is comparable)
  # get rid of the ones with all blank space
  select(!any_of(sub_d %>% keep(~any(is.na(.x))) %>% names)) %>% 
  
# get rid of the irrelevant ones (i.e. extra information)
  select( -one_of(cols)) %>% 
  summarise_all(n_distinct) %>% 
  pivot_longer(cols = everything(), values_to = "n_unique_val", names_to = "name")

level_summary_df %>% 
  filter(n_unique_val != 1) %>% 
  arrange(-n_unique_val)

#moderator
sub_model <- rma.mv(d_calc ~ log(mean_age_months) + mean_production_vocab + native_lang + mean_comprehension_vocab + num_trials + stimuli_naturalness + behavioral_measure +ME_trial_type,
                    V = d_var_calc, 
                    random = ~ 1 | short_cite/same_infant/unique_row, 
                    data = sub_d, 
                    control=list(rel.tol=1e-8)) 



W <- diag(1/sub_model$vi)
X <- model.matrix(sub_model)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
i2 <- sum(sub_model$sigma2) / (sum(sub_model$sigma2) + (sub_model$k-sub_model$p)/sum(diag(P)))
i2

# percentage of change in i2 & the number of moderators added?
```

# Storing additional moderator 

```{r}
age_model_summary <- readRDS(here("cached_data/age_models_df.Rds"))
clean_age_model_summary <- age_model_summary %>% 
  filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(
    REML == min(REML)
  ) %>% 
  select(dataset, model_spec)
```


```{r}
mod_df <- tibble("ds_name" = "Categorization bias", 
       "moderators_no_age" = "test_lang + num_trials + label_present + instruction_code + taxonomic_type + stimuli_naturalness") %>% 
bind_rows(
  tibble("ds_name" = "Online word recognition", 
         "moderators_no_age" = " num_trials + native_lang")
) %>% 
  bind_rows(
    tibble("ds_name" = "Mutual exclusivity", 
           "moderators_no_age" = "mean_production_vocab + native_lang + mean_comprehension_vocab + num_trials + stimuli_naturalness + behavioral_measure +ME_trial_type")
  ) %>% 
  bind_rows(
    tibble("ds_name" = "Mispronunciation sensitivity", 
           "moderators_no_age" = "native_lang + n_feature + mispron_location + type_feature+ dependent_measure + infant_type_language + exposure_phase + CorrectPronunciation + Mispronunciation + is_correct")
  ) %>% 
   bind_rows(
    tibble("ds_name" = "Neonatal Imitation", 
           "moderators_no_age" = "exposure_phase")
  ) %>%  
  bind_rows(
    tibble("ds_name" = "Vowel discrimination (non-native)", 
           "moderators_no_age" = "duration_word_2 + x_dif + F1_2  + F2_1 + F1_2 + F1_1 + duration_word_1 + duration_vowel_2 + duration_vowel_1 + behavioral_measure + response_mode + exposure_phase + counterbalanced + height + nasality + roundness + tenseness + length + peripherality + stimuli_naturalness")
  ) %>% 
   bind_rows(
    tibble("ds_name" = "Neonatal Imitation", 
           "moderators_no_age" = "exposure_phase")
  ) %>% 
  left_join(clean_age_model_summary %>% rename(ds_name = dataset), by = "ds_name") %>% 
  mutate(formula = paste0(model_spec, " + ", moderators_no_age)) %>% 
  select(ds_name, formula)


lapply(seq(nrow(mod_df)), 
       function(x){
         get_ma_effect_size_controlled(d %>% filter(ds_clean == mod_df$ds_name[[x]]), 
                              mod_df$formula[[x]]) %>% 
           mutate(ds_clean = mod_df$ds_name[[x]], 
                  i2_kitchensink = i2) %>% 
           select(ds_clean, i2_kitchensink)
       }) %>% 
  bind_rows() %>% 
  left_join(
    summary_d %>% select(i2), 
    by = "ds_clean"
  )



```


```{r}
get_ma_effect_size_controlled(d %>% filter(ds_clean == mod_df$ds_name[[3]]), 
                               mod_df$formula[[3]])
```


# Overall 

## tau and i^2

```{r}
summary_d %>% 
  select(ds_clean, tau2, i2) %>% 
  pivot_longer(cols = c(tau2, i2), 
               names_to = "value_type", 
               values_to = "val") %>% 
  ggplot(aes(x = reorder(ds_clean, val), y = val)) + 
  geom_point() + 
  coord_flip() + 
  facet_wrap(~value_type, scales = "free")
```


## cv 

```{r}
summary_d %>% 
  mutate(cv = sd / abs(es), 
         sem = cv / sqrt(2*n)) %>% 
  ggplot(aes(x = reorder(ds_clean, cv), y = cv)) + 
  geom_pointrange(aes(ymin = cv - sem, ymax = cv + sem,  alpha = 0.3)) +
  coord_flip() + 
  theme_few() + 
  ylab("")
```

# Controlled for age 

first get the best fitting models 

```{r}
age_model <- readRDS(here("cached_data/min_age_df.RDS"))


age_controlled_estimate <- d %>% 
  group_by(ds_clean) %>% 
  nest(data = -ds_clean) %>% 
  left_join(age_model %>% rename(ds_clean = dataset), by = c("ds_clean")) %>% 
  mutate(mod = map2(data, model_spec, get_ma_effect_size_controlled)) %>% 
  unnest(mod)

```


is the intercept even meaningful? assuming age = 0?

```{r}
age_controlled_estimate %>% 
  ggplot(aes(x = reorder(ds_clean, es), y = es, color = model_spec_clean)) + 
  geom_pointrange(aes(ymin = es_lb, ymax = es_ub, alpha = .3)) + 
  
  coord_flip() + 
  theme_few()
 
```

look at cv
 
```{r}
age_controlled_estimate %>% 
  mutate(cv = sd / abs(es), 
         sem = cv / sqrt(2*n)) %>% 
  ggplot(aes(x = reorder(ds_clean, cv), y = cv)) + 
  geom_pointrange(aes(ymin = cv - sem, ymax = cv + sem,  alpha = 0.3)) +
  coord_flip() + 
  theme_few() + 
  ylab("")
```


comparison 

lol why is controlling age doing more harm than good 
probalby because "But, because the mean bias is very close to zero, the coefficient of variation appears gigantic."???

```{r}
age_controlled_estimate %>% 
  mutate(cv = sd / abs(es), 
         sem = cv / sqrt(2*n)) %>% 
  mutate(cv_type = "age_controlled") %>% 
  bind_rows(
    summary_d %>% 
       mutate(cv = sd / abs(es), 
         sem = cv / sqrt(2*n), 
         cv_type = "plain") 
  ) %>% 
  ggplot(aes(x = reorder(ds_clean, cv), y = cv,  color = cv_type), group = cv_type) + 
  geom_pointrange(aes(ymin = cv - sem, ymax = cv + sem,  alpha = 0.3), position = position_dodge(width = .3)) +
  coord_flip() + 
  theme_few() + 
  ylab("")
```

# Controlled for methods moderators 

## the basic way 

- separate into subgroup and run plain model 

### Behavioral measure 

```{r}
bm <- readRDS(here("cached_data/best_fit_behavioral_measure_df.Rds"))

bm_cv <- d %>% filter(ds_clean %in% (bm %>% distinct(dataset) %>% pull)) %>% 
  group_by(ds_clean, behavioral_measure) %>% 
  nest(data = -c(ds_clean, behavioral_measure)) %>% 
  mutate(mod = map(data, get_ma_effect_size)) %>% 
  unnest(mod) %>% 
  # NA ones are the one with only 1 study left in the grouping
  filter(!is.na(es))

```

```{r}
bm_cv %>% 
   mutate(cv = sd / abs(es), 
         sem = cv / sqrt(2*n)) %>% 
  ggplot(aes(x = reorder(ds_clean, cv), y = cv,  color = behavioral_measure), group = behavioral_measure) + 
  geom_pointrange(aes(ymin = cv - sem, ymax = cv + sem,  alpha = 0.3), position = position_dodge(width = .3)) +
  coord_flip() + 
  theme_few() + 
  ylab("")
```

## Exposure phase 

```{r}
ep <- readRDS(here("cached_data/best_fit_exposure_phase.Rds"))

ep_cv <- d %>% filter(ds_clean %in% (ep %>% distinct(dataset) %>% pull)) %>% 
  group_by(ds_clean, exposure_phase) %>% 
  nest(data = -c(ds_clean, exposure_phase)) %>% 
  mutate(mod = map(data, get_ma_effect_size)) %>% 
  unnest(mod) %>% 
  # NA ones are the one with only 1 study left in the grouping
  filter(!is.na(es))
```


```{r}
ep_cv %>% 
  filter(exposure_phase != "test_only") %>% 
   mutate(cv = sd / abs(es), 
         sem = cv / sqrt(2*n)) %>% 
  ggplot(aes(x = reorder(ds_clean, cv), y = cv,  color = exposure_phase), group = exposure_phase) + 
  geom_pointrange(aes(ymin = cv - sem, ymax = cv + sem,  alpha = 0.3), position = position_dodge(width = .3)) +
  coord_flip() + 
  theme_few() + 
  ylab("")
```



## Stimuli naturalness 
```{r}
rv <- readRDS(here("cached_data/best_fit_real_visual_df.Rds"))
ra <- readRDS(here("cached_data/best_fit_real_aud_df.Rds"))

naturalness_ds <- bind_rows(ra, rv) %>% 
  distinct(dataset)



visual_stimulus_d <- bind_rows((d %>% 
  filter(!is.na(object_stimulus)) %>% 
  #select(ds_clean, object_stimulus) %>% 
  mutate(
    stimulus_naturalness = case_when(
      object_stimulus %in% c("drawings", "digital", "paper",
                             "picture", "word") ~ "artificial", 
      TRUE ~ "natural"
    )
  )), (d %>% 
  filter(!is.na(stimuli_type), ds_clean == "Prosocial agents") %>% 
  mutate(stimulus_naturalness = case_when(
    stimuli_type == "cartoon" ~ "artificial",
    TRUE ~ "natural"
  ))))

aud_stimulus_d <- bind_rows(
  d %>% 
  filter(!is.na(stimuli_type)) %>% 
  filter(ds_clean == "Statistical word segmentation") %>% 
  mutate(stimulus_naturalness = stimuli_type), 
  
  d %>% 
  filter(!is.na(Modality)) %>% 
  mutate(stimulus_naturalness = case_when(
    Modality == "Speech" ~ "natural", 
    TRUE ~ "artificial"
  ))
)

sn_df <- bind_rows(visual_stimulus_d, aud_stimulus_d) %>% 
  group_by(ds_clean, stimulus_naturalness) %>% 
  nest(data = -c("ds_clean", "stimulus_naturalness")) %>% 
  mutate(mod = map(data, get_ma_effect_size)) %>% 
  unnest(mod) %>% 
  # NA ones are the one with only 1 study left in the grouping
  filter(!is.na(es))

```

```{r}
sn_df %>% 
   mutate(cv = sd / abs(es), 
         sem = cv / sqrt(2*n)) %>% 
  ggplot(aes(x = reorder(ds_clean, cv), y = cv,  color = stimulus_naturalness), group = stimulus_naturalness) + 
  geom_pointrange(aes(ymin = cv - sem, ymax = cv + sem,  alpha = 0.3), position = position_dodge(width = .3)) +
  coord_flip() + 
  theme_few() + 
  ylab("")
```








