---
title: "devo curve"
author: "anjie"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: yes
    theme: paper
    toc: yes
    toc_float: yes
---

```{r}
library(tidyverse)
library(here)
library(ggthemes)
library(metafor)
library(ggrepel)

d <- read_csv(here("data/clean_data.csv"))
source(here("helper/model_comparison_help.r"))


```

```{r, setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```



# Vanilla figure 

```{r}
filter(d, 
       mean_age_months < 36) %>%
  ggplot(aes(x = mean_age_months, y = d_calc, 
             weight = 1/d_var_calc)) +
  geom_point(aes(size = 1/d_var_calc),
             alpha = .3) + 
  geom_smooth(method="lm", formula = y ~ x, 
              aes(col = "Linear"), 
              se = FALSE) + 
  geom_smooth(method="lm", formula = y ~ log(x), 
              aes(col = "Log"),
              se = FALSE) + 
  geom_smooth(method="lm", formula = y ~ I(x^2),
              aes(col = "Quadratic"),
              se = FALSE) +
  facet_wrap(~ ds_clean) + 
  geom_hline(yintercept = 0, lty = 2, col = "black") + 
  xlab("Mean age (months)") +
  ylab("Effect size (d)") +
  scale_colour_solarized(name="Models", breaks = c("Linear", "Log",
                                                "Quadratic", "Linear and Log"),
                                     labels=c("Linear" = "Linear",
                                              "Log" = "Log",
                                              "Quadratic" = "Quadratic",
                                              "Linear and Log" = "Linear and Log")) +
  ggthemes::theme_few()
```


# 1. Get Moderators for each dataset


## Kitchen sink: contains all moderators

```{r}

kitchen_sink_df <- lapply((d %>% arrange(ds_clean) %>% distinct(ds_clean)) %>% pull(), 
        function(x){
          get_moderators(x)
        }) %>% 
   bind_rows() 

```

## Key moderators: 

just the ones with some common methodological moderators 

```{r}

key_modearators_df <- d %>% 
  select("ds_clean", "response_mode", "behavioral_measure", "exposure_phase") %>% 
  group_by(ds_clean) %>% 
  summarise_all(n_distinct) %>% 
  pivot_longer(cols = c("response_mode", "behavioral_measure", "exposure_phase"), 
                 names_to = "column_name", 
                 values_to = "n_distinct_value") %>% 
  filter(n_distinct_value!=1) %>% 
  select(-n_distinct_value) %>% 
  nest(moderators =column_name)
  
  
  lapply((d %>% arrange(ds_clean) %>% distinct(ds_clean)) %>% pull(), 
        function(x){
          get_moderators(x)
        }) %>% 
   bind_rows() 
```



# 2. Fitting different types of models 

## Kitchen sink models

```{r}
kitchen_sink_models_df <- lapply(kitchen_sink_df$ds_clean, 
       function(name){
         #print(name)
         tryCatch(get_compare_IC_df(d, name, (kitchen_sink_df %>% filter(ds_clean == name))$moderator_name[[1]] %>% pull()), error = function(e) NULL)
       }) %>% 
  bind_rows()
```


## Key moderators models 

```{r}
key_modearators_model_df <- lapply(key_modearators_df$ds_clean, 
       function(name){
         print(name)
         tryCatch(get_compare_IC_df(d, name, (key_modearators_df %>% filter(ds_clean == name))$moderators[[1]] %>% pull()), error = function(e) NULL)
       }) %>% 
  bind_rows()
```


## age models

```{r}
age_models_df <- lapply(unique(d$ds_clean), 
       function(name){
         print(name)
         get_compare_IC_df(d, name, NULL)
       }) %>% 
  bind_rows()
```



# 3. Model comparison

## compare everything 

currently put together all of the models ran and compare everything 

```{r}

min_AIC_df <- bind_rows(kitchen_sink_models_df, age_models_df, key_modearators_df) %>% 
   filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) 


```

but let's ignore all of those and select the min of all

```{r}
min_AIC_df <- age_models_df %>% mutate(model_type = "base_age") %>% 
  bind_rows(kitchen_sink_models_df %>% mutate(model_type = "kitchen_sink")) %>% 
  bind_rows(key_modearators_model_df %>% mutate(model_type = "key_moderator_df")) %>% 
  filter(ic == "AICc") %>% 
  group_by(dataset) %>% 
  filter(REML == min(REML)) 

min_AIC_df <- min_AIC_df %>% 
  mutate(
    min_AIC_df = case_when(
      model_spec == "d_calc ~ I(mean_age_months^2)" | model_spec == "d_calc ~ log(mean_age_months)" | model_spec == "d_calc ~ mean_age_months" ~ "base_age_model", 
      TRUE ~ "method_moderators_model"
    )
  )

min_AIC_df 
```
## Just compare age base model 

```{r}
min_age_AIC_df <- age_models_df %>% 
  group_by(dataset) %>% 
  filter(ic == "AICc") %>% 
  filter(REML == min(REML)) 

min_age_AIC_df %>% kableExtra::kable()
```




# 4. Get Prediction

```{r}
min_AIC_df %>% 
  rename(ds_name = dataset) %>% 
  mutate(
    ds_type = case_when(
      ds_name %in% c("Familiar word recognition", 
                     "Infant directed speech preference", 
                     "Language discrimination and preference", 
                     "Mispronunciation sensitivity", 
                     "Natural speech preference", "Sound symbolism",
                     "Statistical sound category learning (habituation)",
                     "Statistical word segmentation",
                     "Vowel discrimination (native)",
                     "Vowel discrimination (non-native)" ,"Word Segmentation (combined)" ) ~ "Language - perceptual", 
      ds_name %in% c("Cross-situational word learning", 
                      "Label advantage in concept learning",
                     "Mutual exclusivity",
                     "Online word recognition",
                     "Switch task",
                     "Syntactic bootstrapping" 
                     ) ~ "Language - conceptual", 
      ds_name %in% c("Gaze following (combined)", "Prosocial agents") ~ "Social",
      ds_name %in% c("Abstract rule learning",  "Categorization bias", 
                     "Simple arithmetic competences", "Symbolic play") ~ "Cognitive"
     )
  ) %>% 
  group_by(ds_type, model_type) %>% 
  count() %>% 
  kableExtra::kable()
```




## Just age

```{r}
min_age_AIC_df <- age_models_df %>% 
  group_by(dataset) %>% 
  filter(ic == "AICc") %>% 
  filter(REML == min(REML)) 


saveRDS(min_age_AIC_df, here("cached_data/min_age_df.RDS"))
min_age_df <- readRDS(here("cached_data/min_age_df.RDS"))


all_age_pred <- lapply(seq(1, nrow(min_age_df)), 
       function(x){
         get_age_model_prediction(min_age_df$dataset[[x]], min_age_df, d)
       }) %>% 
  bind_rows() 

saveRDS(all_age_pred, here("cached_data/min_age_pred_df.RDS"))
```

categorize 

```{r message=FALSE, warning=FALSE}



categorized_age_pred_df <- all_age_pred %>% 
  select(pred, ds_name) %>% 
  group_by(ds_name) %>% 
  mutate(mean_age_months = (row_number() + 1) / 2) %>% 
  mutate(
    ds_type = case_when(
      ds_name %in% c("Familiar word recognition", 
                     "Infant directed speech preference", 
                     "Language discrimination and preference", 
                     "Mispronunciation sensitivity", 
                     "Natural speech preference", "Sound symbolism",
                     "Statistical sound category learning (habituation)",
                     "Statistical word segmentation",
                     "Vowel discrimination (native)",
                     "Vowel discrimination (non-native)" ,"Word Segmentation (combined)" ) ~ "Language - perceptual", 
      ds_name %in% c("Cross-situational word learning", 
                      "Label advantage in concept learning",
                     "Mutual exclusivity",
                     "Online word recognition",
                     "Switch task",
                     "Syntactic bootstrapping" 
                     ) ~ "Language - conceptual", 
      ds_name %in% c("Gaze following (combined)", "Prosocial agents") ~ "Social",
      ds_name %in% c("Abstract rule learning",  "Categorization bias", 
                     "Simple arithmetic competences", "Symbolic play") ~ "Cognitive"
     )
  ) %>% 
  
  select(ds_name, ds_type, mean_age_months, pred) 



label_df <- categorized_age_pred_df %>% 
  filter(mean_age_months == 30)


p <- categorized_age_pred_df %>% 
  ggplot(aes(x = mean_age_months, y = pred, group = ds_name, color = ds_name)) + 
  geom_label_repel(data = label_df, aes(x = mean_age_months, y = pred, label = ds_name, 
                                      
                                       box.padding = 0.3), 
                   size = 2, 
                   position = "jitter",
                   force = 1100, 
                   max.overlaps = Inf,
                    expand = expansion(mult = 0.5)) + 
  geom_line(alpha = .8)+ 
  facet_wrap(~ds_type) + 
  theme_few()+
  theme(legend.position = "none") 
  

p

```


```{r}
age_range_df <- d %>% 
  group_by(ds_clean) %>% 
  summarise(min_age = min(mean_age_months, na.rm = TRUE), 
            max_age = max(mean_age_months, na.rm = TRUE)) %>% 
  rename(ds_name = ds_clean)
```



```{r}


categorized_age_pred_df <- all_age_pred %>% 
  select(pred, ds_name) %>% 
  group_by(ds_name) %>% 
  mutate(mean_age_months = (row_number() + 1) / 2) %>% 
  left_join(age_range_df, by = c("ds_name")) %>% 
  filter(mean_age_months > min_age, 
         mean_age_months < min(36, max_age)) %>% 
  mutate(
    ds_type = case_when(
      ds_name %in% c( "Language discrimination and preference", 
                     "Mispronunciation sensitivity", 
                     "Natural speech preference", "Sound symbolism", "Statistical sound category learning (habituation)", 
                     "Vowel discrimination (native)",
                     "Vowel discrimination (non-native)" ,"Word Segmentation (combined)",
                     "Statistical word segmentation") ~ "Sounds", 
      
      ds_name %in% c("Familiar word recognition", 
                     "Cross-situational word learning", 
                      "Label advantage in concept learning",
                     "Mutual exclusivity",
                     "Online word recognition",
                     "Syntactic bootstrapping",
                     "Switch task") ~ "Words",
      
      ds_name %in% c("Gaze following (combined)",
                     "Prosocial agents",
                     "Symbolic play", 
                     "Infant directed speech preference") ~ "Communication", 
      
      ds_name %in% c("Abstract rule learning",  
                     "Categorization bias", 
                     "Simple arithmetic competences") ~ "Cognitive"
     )
  ) %>% 
  mutate(pred = case_when(
    ds_name == "Abstract rule learning" ~ -pred, 
    ds_name == "Switch task" ~ -pred,
    TRUE ~ pred
  )) %>% 
  select(ds_name, ds_type, mean_age_months, pred) 



label_df <- categorized_age_pred_df %>% 
  filter(mean_age_months == max(mean_age_months)) 

label_df$x = c(
  13 + 2, 
  35.5 + 2, 
  35.5 + 4, 
  15 + 2, 
  23.5, 
  18.5 + 12, 
  17.5 - 8, 
  11.5 , # problem
  35.5 + 4,
  35.5,
  12.5 + 5,
  30.0,
  31.5 + 8, 
  9 + 4, 
  35.5 + 8,
  11 + 3, 
  18.5 + 10, 
  24.5, 
  35.5 + 5, 
  35.5 + 3, 
  29.5 + 10, 
  17.5 + 22, 
  24.5 + 15
  
)
label_df$y = c(
  0.05004268 - 0.5, 
  0.27548039 + 0.3, 
  0.54489342 - 0.2, 
  0.80489381 + 0.6, 
  2.98616109 + 0.3, 
  1.43817970 + 0.3,
  0.52126530 + 0.5, 
  0.26533988 - 0.8, 
  1.61860775 + 0.3,
  1.44122780 + 0.3,
  0.81136554 + 0.3,
  2.96433139 + 0.5,
  0.3505974, 
  0.3903635 + 0.5,
  0.3828921 - 0.1, 
  0.9685146 + 0.6, 
  -0.3027715 + 0.1, 
  0.3034464 - 0.6, 
  0.6137494 + 0.3, 
  0.1028029 - 0.2, 
  0.5170778 + 0.8, 
  0.4909005 + 0.5, 0.2914371 + 0.3
  
)

p <- categorized_age_pred_df %>% 
  ggplot(aes(x = mean_age_months, y = pred, group = ds_name, color = ds_name)) + 
  geom_hline(yintercept = 0, linetype = "dashed", alpha = .5) + 
  geom_line(alpha = 1, width = 2)+ 
  geom_text(data = label_df, aes(x = x, y = y, label = ds_name), 
                   size = 2.2,
                  segment.color = NA) + 
  xlim(0, 48) + 
  ylim(-2, 4) + 
  facet_wrap(~ds_type, scales = "free") + 
  theme_few()+
  theme(legend.position = "none") + 
  xlab("Age (months)") + 
  ylab("Predicted Value")
  

p
#label_df$ds_name
```

```{r}
categorized_age_pred_df %>% 
  filter(ds_name == "Language discrimination and preference") %>% 
  ggplot(aes(x = mean_age_months, y = pred, group = ds_name, color = ds_name))  + 
  geom_point()
```



## with method

```{r}
min_AIC_df
```



# Draft for adding method moderators 

summary(model)$X.f for coding 

drop the rows that's dropped when fitting models:
  current_df$keep = model$not.na
  current_df = current_df[current_df$keep, ]
  

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
test_d <- d %>% filter(ds_clean == "Gaze following (combined)")
test_d <- test_d %>% mutate(cue_type = as.factor(cue_type))

contrasts(test_d$cue_type) <-  contr.sum(4)




res_m_method <- rma.mv(d_calc ~ mean_age_months + cue_type, 
    V = d_var_calc, 
    random = ~ 1 | short_cite/same_infant/unique_row, 
    data = test_d)

res_m_method_log <- rma.mv(d_calc ~ log(mean_age_months) + cue_type, 
    V = d_var_calc, 
    random = ~ 1 | short_cite/same_infant/unique_row, 
    data = test_d)

res_method_square <-  rma.mv(d_calc ~ I(mean_age_months^2) + cue_type, 
    V = d_var_calc, 
    random = ~ 1 | short_cite/same_infant/unique_row, 
    data = test_d)

p.res_method <- predict(res_m_method, addx =TRUE) %>% as.data.frame()
p.res_method_log <- predict(res_m_method_log, addx = TRUE) %>% as.data.frame()
p.res_method_square <- predict(res_method_square, addx = TRUE) %>% as.data.frame()

prediction_df <- p.res_method %>% 
  rename(p.linear = pred)

prediction_df$p.log = p.res_method_log$pred
prediction_df$p.square = p.res_method_square$pred



prediction_df %>% 
  pivot_longer(cols = starts_with("p."), 
               names_to = "prediction_type", 
               values_to = "prediction_val") %>% 
  ggplot(aes(x = X.mean_age_months, y = prediction_val, color = prediction_type)) + 
  geom_point() + 
  facet_wrap(~prediction_type)

  left_join(p.res_method_log
            %>% rename(p.log = pred), 
            by = c("X.intrcpt", "X.mean_age_months", "X.cue_type1", "X.cue_type2", "X.cue_type3")) %>% 
  left_join(p.res_method_square %>% rename(p.square = pred), 
            by = c("X.intrcpt", "X.mean_age_months", "X.cue_type1", "X.cue_type2", "X.cue_type3"))





```

