
```{r}
library(tidyverse)
library(here)
library(lme4)
library(metafor)
library(ggthemes)
library(boot)

source(here("analysis/helper/model_comparison_help.r"))
source(here("analysis/helper/bootsrap_ci.R"))

d <- read_csv(here("data/metalab_data_kitchensink.csv"))
method_d <- (read_csv(here("data/ks_info.csv"))) %>% 
  filter(!is.na(var)) 
```



# Caching Results 


## Dataframe: Multiple age groups + Single Method 

```{r}
study_with_multiple_age_group_d <- d %>% 
  group_by(ds_clean, short_cite) %>%
  filter(mean_age_months < 48) %>% 
  summarise(
    max_mean_age_months = max(mean_age_months), 
    min_mean_age_months = min(mean_age_months)
  ) %>% 
  mutate(diff = max_mean_age_months - min_mean_age_months) %>% 
  filter(diff > 1) %>% 
  distinct(ds_clean, short_cite) %>% 
  ungroup()



var_selection <- method_d %>%
  filter(!is.na(var)) %>% 
  # Split the column values and unnest to keep them in a list-column
  mutate(cols = str_split(`var`, " \\+ ")) %>% 
  mutate(cols =  lapply(cols, function(x) gsub("\\s+", "", x)))


study_with_single_method_d <- lapply(
  seq(1, nrow(method_d)), 
  function(id){
    d %>%
    filter(ds_clean == var_selection$ds_clean[[id]]) %>% 
    select(
      ds_clean,
      short_cite, 
      all_of(var_selection$cols[[id]])) %>% 
    mutate_if(is.numeric, as.character) %>% 
    rowwise() %>%
    mutate(meta_method = paste(c_across(-c(ds_clean, short_cite)), collapse = ";")) %>% 
    distinct(ds_clean, meta_method, short_cite) %>% 
    group_by(ds_clean, short_cite) %>% 
    count()
  }
) %>% 
  bind_rows() %>% 
  filter(n == 1) %>% 
  rename(n_method_group = n)

single_method_multiple_age <- study_with_single_method_d %>% 
  filter(short_cite %in% study_with_multiple_age_group_d$short_cite)

write_rds(single_method_multiple_age, here("cached_data/single_method_multiple_age.Rds"))

```


## Nilam's suggested analysis

```{r}
d %>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_point(alpha = .5) + 
  geom_line(aes(group = study_ID), alpha = .5)+
  facet_wrap(~ds_clean, scales = "free_x")
```

```{r fig.height=8, fig.width=10}
d %>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm") + 
  geom_line(aes(group = short_cite), alpha = .5)+
  facet_wrap(~ds_clean, scales = "free")
```


### run the models

```{r}
better_half_nested_half_d <- read_rds(here("cached_data/better_halves_data.Rds"))%>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  group_by(ds_clean, ds_half) %>% 
  nest()

better_half_same_method_model <- nested_half_d %>% 
  filter(!(ds_clean == "Sound symbolism" & ds_half == "Sound symbolism_half1")) %>% 
  mutate(
    model = (map(data, ~ broom.mixed::tidy(metafor::rma.mv(d_calc ~ mean_age_months, 
                         V = d_var_calc, 
                          random = ~ 1 | short_cite/same_infant/unique_row, 
                          data = .), conf.int = TRUE)))
    
    ) %>% 
  unnest(model)

full_nested_d <- d%>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  group_by(ds_clean) %>% 
  nest()

full_same_method_model <- full_nested_d %>% 
  #filter(!(ds_clean == "Sound symbolism" & ds_half == "Sound symbolism_half1")) %>% 
  mutate(
    model = (map(data, ~ broom.mixed::tidy(metafor::rma.mv(d_calc ~ mean_age_months, 
                         V = d_var_calc, 
                          random = ~ 1 | short_cite/same_infant/unique_row, 
                          data = .),  conf.int = TRUE)))
    
    ) %>% 
  unnest(model)
```

```{r fig.width=12}
full_slope_estimates <- readRDS(here("cached_data/all_slope_estimates.Rds")) %>% 
  filter(term == "mean_age_months") %>% 
  mutate(type = "original") %>% 
  rename(ds_clean = dataset)

full_same_methods_estimates <- full_same_method_model %>% 
  filter(term == "mean_age_months") %>% 
  mutate(type = "all same methods")

better_half_same_methods_estimates <- better_half_same_method_model %>% 
  filter(term == "mean_age_months") %>% 
  mutate(type = "better half same method")

bind_rows(full_slope_estimates, full_same_methods_estimates, better_half_same_methods_estimates) %>% 
  ggplot(aes(x = ds_clean, y = estimate, ymin = conf.low, ymax = conf.high, color = type)) + 
  geom_pointrange(position = position_dodge(width = .5)) + 
  geom_hline(yintercept = 0, color = "gray", linetype = "dashed") + 
  theme_few() + 
  coord_flip()


bind_rows(full_slope_estimates, full_same_methods_estimates, better_half_same_methods_estimates) %>% 
  mutate(is_sig = (p.value < 0.05)) %>% 
  ggplot(aes(x = ds_clean, y = estimate, ymin = conf.low, ymax = conf.high, color = is_sig)) + 
  geom_pointrange(position = position_dodge(width = .5)) + 
  geom_hline(yintercept = 0, color = "gray", linetype = "dashed") + 
  theme_few() + 
  coord_flip() + 
  facet_wrap(~type)


```

```{r}

```



```{r}
read_rds(here("cached_data/better_halves_data.Rds")) %>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_smooth(method = "lm") + 
  geom_point(alpha = .5) + 
  geom_line(aes(group = short_cite), alpha = .5)+
  facet_wrap(~ds_half, scales = "free")
```


maybe just get the ones with larger effect sizes?

```{r}
good_studies <- read_rds(here("cached_data/better_halves_data.Rds")) %>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  select(ds_clean, ds_half, short_cite, study_ID, mean_age_months, d_calc) %>%  
  group_by(ds_clean, ds_half, short_cite, study_ID) %>% 
  mutate(
    min_age = min(mean_age_months), 
    max_age = max(mean_age_months), 
    min_es = min(d_calc), 
    max_es = max(d_calc),
    row_id = row_number()
  ) %>% 
  # does the one with the largest age also have the largst ES
  filter(d_calc == max_es) %>% 
  filter(max_age == mean_age_months) %>% 
  ungroup() %>% 
  select(ds_clean, ds_half, short_cite, study_ID)


read_rds(here("cached_data/better_halves_data.Rds")) %>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  filter(ds_half %in% good_studies$ds_half, 
         short_cite %in% good_studies$short_cite) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_point(alpha = .5) + 
  geom_line(aes(group = short_cite), alpha = .5)+
  facet_wrap(~ds_half, scales = "free")
  
```


## fit (age|short_cite) model

### Figure out datasets that allow us to run this 

```{r}

pruned_df <- d %>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  group_by(ds_clean) %>% 
  count() 

nested_d <- d %>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  group_by(ds_clean) %>%
 nest() %>% 
  mutate(
    n_row = map(data, ~ count(.) %>% pull(n)), 
    n_group = map(data, ~ distinct(., short_cite) %>% count() %>% pull(n))
  ) %>% 
  unnest(n_row, n_group) %>% 
  # this is to foucs on studies with enough data
  filter(n_row > 20) 

# run the models 
pruned_model <- lapply(seq(1, nrow(nested_d)), 
       function(id){
         print(nested_d$ds_clean[[id]])
         data = nested_d$data[[id]]
         model = lmerTest::lmer(d_calc ~ mean_age_months + (mean_age_months | short_cite), data = data, 
                                control = lme4::lmerControl(optimizer="bobyqa"))
         res = broom.mixed::tidy(model) %>% mutate(ds_clean = nested_d$ds_clean[[id]]) %>% 
           mutate(isSingular = lme4::isSingular(model))
         return(res)
      }) %>% 
  bind_rows()


rma.mv(as.formula(formula), 
                    V = d_var_calc, 
                    random = ~ 1 | short_cite/same_infant/unique_row, 
                    data = current_df)


```

### focus on the ones that does not give isSingular warning 

```{r}
general_coef <- pruned_model %>% 
  filter(isSingular == FALSE) %>% 
  filter(term == "mean_age_months") %>% 
  select(ds_clean, estimate, std.error) %>% 
  mutate(estimate_lb  = estimate - 1.96 * std.error, 
         estimate_ub = estimate + 1.96 * std.error)

coef_data <- nested_d %>% 
  filter(ds_clean %in% general_coef$ds_clean) 
  
group_specific_estimate <- lapply(seq(1, nrow(coef_data)), 
       function(id){
         print(coef_data$ds_clean[[id]])
         data = coef_data$data[[id]]
         model = lmerTest::lmer(d_calc ~ mean_age_months + (mean_age_months | short_cite), data = data, 
                                control = lme4::lmerControl(optimizer="bobyqa"))
         res = lme4::ranef(model)[[1]] %>% as.data.frame() %>% 
           mutate(ds_clean = coef_data$ds_clean[[id]])
         return(res)
      }) %>% 
  bind_rows() %>% 
  left_join(general_coef, by = c("ds_clean")) %>% 
  mutate(group_specific_estimate = mean_age_months + estimate)



all_ci_estimate_data <- lapply(seq(1, nrow(coef_data)), 
       function(id){
         data = coef_data$data[[id]]
         name = coef_data$ds_clean[[id]]
         print(name)
         estimates = get_ci_for_random_slope(name, data, 5000)
         return (estimates)
       }) %>% bind_rows()


 
all_info_d <- group_specific_estimate %>% 
  group_by(ds_clean) %>% 
  mutate(group_id = row_number()) %>% 
  left_join(all_ci_estimate_data %>% rename(ds_clean = ds_name), by = c("ds_clean", "group_id")) %>% 
  left_join(coef_data %>% unnest(data) %>% distinct(ds_clean, short_cite) %>% group_by(ds_clean) %>% mutate(group_id = row_number()), 
            by = c("ds_clean", "group_id"))  



```

### Cache results

```{r}
write_rds(all_info_d, here("cached_data/group_specific_estimate.Rds"))
```


## Delta age model 

```{r}

delta_age <-  d %>% 
  filter(ds_clean %in% (single_method_multiple_age %>% ungroup() %>%  distinct(ds_clean) %>% pull()), 
         short_cite %in% (single_method_multiple_age %>% ungroup() %>%  distinct(short_cite) %>% pull())) %>% 
  group_by(ds_clean, short_cite) %>% 
  summarise(min_age = min(mean_age_months)) %>% 
  left_join(d %>% 
  filter(ds_clean %in% (single_method_multiple_age %>% ungroup() %>%  distinct(ds_clean) %>% pull()), 
         short_cite %in% (single_method_multiple_age %>% ungroup() %>%  distinct(short_cite) %>% pull())), 
  by = c("ds_clean", "short_cite")) %>% 
  select(ds_clean, short_cite, mean_age_months, same_infant, unique_row, min_age, d_calc, d_var_calc) %>% 
  mutate(delta_age = mean_age_months - min_age)



delta_age_model <- lapply(
  seq(1, nrow(delta_age %>% distinct(ds_clean))), 
  function(x){
    get_model_fit_df(delta_age, ds_name = (delta_age %>% distinct(ds_clean) %>% pull())[[x]], NULL, 
                     age_type = "delta_age")
  }
) %>% 
  bind_rows()

write_rds(delta_age_model, here("cached_data/delta_age.Rds"))
```



## talk visualization 

```{r fig.width=10, fig.height = 6}
delta_age_model %>% 
  filter(term == "delta_age") %>% 
  mutate(conf.low = estimate - 1.96 * std.error, 
         conf.high = estimate + 1.96 * std.error) %>% 
  select(term, estimate, conf.low, conf.high, p.value, dataset) %>% 
  bind_rows(
    all_slope_estimates %>% 
  filter(term == "mean_age_months") %>% 
  select(term, estimate, conf.low, conf.high, p.value, dataset)
  ) %>% 
  mutate(term = if_else(term == "delta_age", "Same Method Delta Age", "Original")) %>% 
  ggplot(aes(x = dataset, y = estimate)) + 
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = term),
                  position = position_dodge(width = .5)) + 
  scale_color_manual(values = c("purple", "lightblue")) + 
  geom_hline(yintercept = 0, color = "gray", linetype = "dashed") + 
  coord_flip() + 
  theme_few() + 
  xlab("") + 
  ylab("Estimate on Age") + 
  theme(legend.position = "top") + 
  scale_color_discrete(name = "")



```




# Visualization 

## (age|short_cite)

```{r}
all_info_d <- readRDS(here("cached_data/group_specific_estimate.Rds"))

tidy_all_info_d <- all_info_d %>% distinct(ds_clean, estimate, estimate_ub, estimate_lb) %>% 
  mutate(short_cite = "General", 
         estimate_type = "general_estimate") %>%
  rename(ci_lower = estimate_lb, 
         ci_upper = estimate_ub) %>% 
  bind_rows(
    all_info_d %>% distinct(ds_clean, group_specific_estimate, ci_lower, ci_upper, group_id, short_cite) %>% 
      rename(estimate = group_specific_estimate) %>% 
      mutate(estimate_type = "group_specific_estimate")
  ) 

top_group <- tidy_all_info_d[tidy_all_info_d$short_cite == "General", ]
tidy_all_info_d <- tidy_all_info_d[tidy_all_info_d$short_cite != "General", ]
tidy_all_info_d <- tidy_all_info_d[order(-tidy_all_info_d$estimate), ]
tidy_all_info_d <- rbind(top_group, tidy_all_info_d)
tidy_all_info_d$short_cite <- factor(tidy_all_info_d$short_cite , levels = unique(tidy_all_info_d$short_cite))


tidy_all_info_d %>% 
  ggplot(aes(x = short_cite, y = estimate, ymin = ci_lower, ymax = ci_upper, color = estimate_type)) + 
  geom_pointrange() + 
   geom_hline(aes(yintercept = 0), alpha = .3, color = "red", linetype = "dashed") + 
  facet_wrap(~ds_clean, scales = "free", nrow = 2) + 
  theme_few()+ 
  theme(legend.position = "bottom") +
  coord_flip() + 
  xlab("") + 
  ylab("Estimate for Mean age months")
```

## Delta age 

```{r}

single_method_multiple_age <- readRDS(here("cached_data/single_method_multiple_age.Rds"))

d %>% 
  filter(ds_clean %in% (single_method_multiple_age %>% ungroup() %>%  distinct(ds_clean) %>% pull()), 
         short_cite %in% (single_method_multiple_age %>% ungroup() %>%  distinct(short_cite) %>% pull())) %>% 
  group_by(ds_clean, short_cite) %>% 
  summarise(min_age = min(mean_age_months)) %>% 
  left_join(d %>% 
  filter(ds_clean %in% (single_method_multiple_age %>% ungroup() %>%  distinct(ds_clean) %>% pull()), 
         short_cite %in% (single_method_multiple_age %>% ungroup() %>%  distinct(short_cite) %>% pull())), 
  by = c("ds_clean", "short_cite")) %>% 
  select(ds_clean, short_cite, mean_age_months, min_age, d_calc, d_var_calc) %>% 
  mutate(delta_age = mean_age_months - min_age) %>% 
  ggplot(aes(x = delta_age, y = d_calc)) + 
  geom_point() + 
  geom_line(aes(group  = short_cite)) +
  facet_wrap(~ds_clean, scales = "free") + 
  theme_few() + 
  geom_smooth(method = "lm") + 
  theme(strip.text.x = element_text(size = 5))
```


```{r}
delta_age_model_df <- d %>% 
  filter(ds_clean %in% (single_method_multiple_age %>% ungroup() %>%  distinct(ds_clean) %>% pull()), 
         short_cite %in% (single_method_multiple_age %>% ungroup() %>%  distinct(short_cite) %>% pull())) %>% 
  group_by(ds_clean, short_cite) %>% 
  summarise(min_age = min(mean_age_months)) %>% 
  left_join(d %>% 
  filter(ds_clean %in% (single_method_multiple_age %>% ungroup() %>%  distinct(ds_clean) %>% pull()), 
         short_cite %in% (single_method_multiple_age %>% ungroup() %>%  distinct(short_cite) %>% pull())), 
  by = c("ds_clean", "short_cite")) %>% 
  select(ds_clean, short_cite, mean_age_months, min_age, d_calc, d_var_calc, short_cite, same_infant, unique_row) %>% 
  mutate(delta_age = mean_age_months - min_age) %>% 
  group_by(ds_clean) %>% 
  nest() %>% 
  mutate(
    model = map(data, ~broom::tidy(rma.mv(d_calc ~ delta_age, 
                             V = d_var_calc, 
                             random = ~ 1 | short_cite/same_infant/unique_row, 
                             data = .)))
  ) %>% 
  unnest(model) %>% 
  filter(term == "delta_age") 


delta_age_model_df %>% 
  filter(p.value < .05)
```




# Misc 


```{r }
pruned_more_model <- lapply(seq(1, nrow(pruned_more_nested)), 
       function(id){
         print(pruned_more_nested$ds_clean[[id]])
         data = pruned_more_nested$data[[id]]
         model = lm(d_calc ~ mean_age_months, data = data)
         res = broom::tidy(model) %>% mutate(ds_clean = pruned_more_nested$ds_clean[[id]])
         return(res)
      }) %>% 
  bind_rows() %>% 
  mutate(model_spec = "d_calc ~ mean_age_months")
  
bind_rows(pruned_model, pruned_more_model) %>% 
  filter(term == "mean_age_months") %>% 
  mutate(
    lb = estimate - std.error * 1.96, 
    ub = estimate + std.error * 1.96
  ) %>% 
  select(ds_clean, estimate, lb, ub, p.value) %>% 
  mutate(sig = if_else(p.value < .05, "sig", "non_sig")) %>% 
  ggplot(aes(x = reorder(ds_clean, estimate), y = estimate, ymin = lb, ymax = ub, color = sig)) + 
  geom_hline(yintercept = 0, color = "gray", alpha = .5, linetype = "dashed") + 
  geom_pointrange() + 
  theme_few() + 
  coord_flip() + 
  xlab("") + 
  ylab("Estimate (mean age in months)") 

  
```



```{r}
d %>% 
  filter(ds_clean %in% single_method_multiple_age$ds_clean, 
         short_cite %in% single_method_multiple_age$short_cite) %>% 
  filter(ds_clean == "Natural speech preference")
```



## multiple methods case

```{r}
# all of the studies with both multiple age groups and multiple methods!
multimulti_df <- lapply(
  seq(1, nrow(method_d)), 
  function(id){
    d %>%
    filter(ds_clean == var_selection$ds_clean[[id]]) %>% 
    mutate(method_name = paste(var_selection$cols[[id]], collapse = ";")) %>% 
    select(
      ds_clean,
      short_cite, 
      method_name, 
      all_of(var_selection$cols[[id]])) %>% 
    mutate_if(is.numeric, as.character) %>% 
    rowwise() %>%
    mutate(meta_method = paste(c_across(-c(ds_clean, method_name, short_cite)), collapse = ";")) %>% 
      select(ds_clean, short_cite, method_name, meta_method)
  }
) %>% bind_rows() %>% 
  distinct(ds_clean, short_cite, method_name, meta_method) %>% 
  filter(ds_clean %in% multiple_d$ds_clean, 
         short_cite %in% multiple_d$short_cite) %>% 
  arrange(ds_clean, short_cite)
```


```{r}
changed_methods_df <- multimulti_df %>% 
  group_by(ds_clean, short_cite, method_name) %>%
  # Split each string into words and capture their position
  mutate(methods = str_split(meta_method, ";"),
         method_name = str_split(method_name, ";"),
         position = map(meta_method, ~seq_along(.x))) %>%
  unnest(c(methods, method_name, position)) %>%
  select(-meta_method) %>% 
  # Tally words for each position
  count(position, methods, name = "n") %>%
  # Filter for positions with more than one unique word
  group_by(position, ds_clean, short_cite) %>%
  filter(n_distinct(words) > 1) %>%
  arrange(position, desc(n)) %>% 
  filter(n ==1) 


grouping_df <- changed_methods_df %>% distinct(ds_clean, short_cite, method_name) %>% 
  group_by(ds_clean, short_cite) %>%
  summarise(method_list = list(method_name))

grouping_df

nested_df <- d %>% 
  filter(ds_clean %in% grouping_df$ds_clean, 
         short_cite %in% grouping_df$short_cite) %>% 
  group_by(ds_clean, short_cite) %>% 
  nest() 


calculate_one_group <- function(ds, ds_name, short_cite_name, method_name_list){
  sub_df <- ds %>% filter(ds_clean == ds_name, short_cite == short_cite_name)
  method_age_res <- lapply(method_name_list, 
                           function(name){
                             
                             group_ <- syms(name)
                      
                             sub_df %>% 
                               #select(!!name)
                               group_by(!!!group_) %>% 
                               summarise(
                                 mean_age_method_group = mean(mean_age_months, na.rm = TRUE), 
                                 sd_age_method_group = sd(mean_age_months, na.rm = TRUE)
                               ) %>% 
                               mutate(method_name = as.character(name), 
                                      method = !!group_)
            
                 }) %>% 
    bind_rows() %>% 
    mutate(ds_clean = ds_name, short_cite = short_cite_name)
  
  return (method_age_res)
 
}

main_df <- lapply(
  seq(1, nrow(grouping_df)), 
      function(id){
        calculate_one_group(d, grouping_df$ds_clean[[id]], grouping_df$short_cite[[id]], 
                    grouping_df$method_list[[id]])
      }) %>% bind_rows()

main_df %>% 
  select(ds_clean, short_cite, method_name, mean_age_method_group, sd_age_method_group) %>% 
  ggplot(aes(x = method_name, y = mean_age_method_group, color = method_name)) + 
  geom_point() + 
  facet_wrap(short_cite~ds_clean, scales = "free")  + 
  theme(legend.position = "none")
  
```







```{r}
# first figure out study with actual methodological changes between condition  

method_change_d <- test_d %>% 
  mutate(mega_method = paste(stimuli_naturalness, Semantics, Modality, exposure_phase, method, sep = "_")) %>% 
  group_by(short_cite, mega_method) %>% 
  count() %>% 
  group_by(short_cite) %>% 
  count() %>% 
  filter(n > 1) %>% 
  pull(short_cite)

test_d %>% 
  filter(short_cite %in% method_change_d) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = stimuli_naturalness)) + 
  geom_point() + 
  facet_wrap(~short_cite)

test_d %>% 
  filter(short_cite %in% method_change_d) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = Semantics)) + 
  geom_point() + 
  facet_wrap(~short_cite)

test_d %>% 
  filter(short_cite %in% method_change_d) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = Modality)) + 
  geom_point() + 
  facet_wrap(~short_cite)

test_d %>% 
  filter(short_cite %in% method_change_d) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = exposure_phase)) + 
  geom_point() + 
  facet_wrap(~short_cite)

test_d %>% 
  filter(short_cite %in% method_change_d) %>% 
  ggplot(aes(x = mean_age_months, y = d_calc, color = method)) + 
  geom_point() + 
  facet_wrap(~short_cite)
```

a1: we don't see much evidence for condition change within a study, not as a function of age. 


some sort of ad hoc binning of age 

what's the best way to summarise this information quantitatively??? or do we need to? 


## Across study 

```{r}


test_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_point(aes(size = n_1 / 10)) + 
  geom_smooth(method = "lm") + 
  facet_wrap(~stimuli_naturalness)

test_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_point(aes(size = n_1 / 10)) + 
  geom_smooth(method = "lm") + 
  facet_wrap(~Semantics)

test_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_point(aes(size = n_1 / 10)) + 
  geom_smooth(method = "lm") + 
  facet_wrap(~Modality)

test_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_point(aes(size = n_1 / 10)) + 
  geom_smooth(method = "lm") + 
  facet_wrap(~exposure_phase)
  

test_d %>% 
  ggplot(aes(x = mean_age_months, y = d_calc)) + 
  geom_point(aes(size = n_1 / 10)) + 
  geom_smooth(method = "lm") + 
  facet_wrap(~method)
  
```






